Thermal reactionomes reveal adaptive responses to thermal extremes in warm

### 2014-10-20 doc/ApTranscriptome_manuscript.Rmd
cleaning up Rmd file so it compiles

---
title: Thermal reactionomes reveal adaptive responses to thermal extremes in warm
  and cool-climate ant species
author: ' '
csl: ecology.csl
output:
  word_document: default
  pdf_document:
    fig_caption: yes
    includes:
      in_header: header.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc_depth: 2
  html_document: null
includes: header.tex
bibliography: ApTranscriptome.bib
---

@@

![Figure 1](matched_observations_Fig1.tiff)

![Figure 2](crit_temp_regulation_Fig2.tiff)

![Figure 3](constitutive_vs_upreg_Fig3.tiff)

>>>>

---
title: Thermal reactionomes reveal adaptive responses to thermal extremes in warm
  and cool-climate ant species
author: ' '
csl: ecology.csl
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: header.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc_depth: 2
  html_document: null
  word_document: default
includes: header.tex
bibliography: ApTranscriptome.bib
---

@@

![Matched expression type data for *A. carolinensis* (rows) and *A. picea* (columns). The color of each cell represent the deviation of the observed from the expected number of transcripts based on hypothetical equivalence of the marginal frequencies. Blue cells are those with significant excesses, while red cells are those with significant absences.](../results/matched_observations_Fig1.png)

![Histogram with smooth density estimate of temperature of maximum change in expression for transcripts that have increased expression at **Low** and **High** temperatures. Red bars and lines are for *A. carolinensis* while blue bars and lines are for *A. picea*.](../results/crit_temp_regulation_Fig2.png)

![Scatterplots of (A) constitutive expression in *A. picea* against degree of induction for upregulated transcripts in *A. carolinensis* and (B) constitutive expression in *A. carolinensis* against degree of induction for upregulated transcripts in *A. picea.*. For each species, the transcripts are split into expression category based on the ... The top row is for *High* transcripts, middle is for *Intermediate* transcripts and bottom row is for *Low* transcripts.](../results/constitutive_vs_upreg_Fig3.png)
